Stochastic Wind Power Forecasting

### 2020-04-25 LaTeX_Code/Paper/paper_1line_Renzo.tex

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
\label{fig:neg-LL}
\end{figure}
On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
\begin{table}[]
\centering
\begin{tabular}{lccc}
\toprule
 & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
 \midrule
 Initial guess & 1.629 & 0.060 & 0.098 \\
 fminsearch & 1.135 & 0.073 & 0.083 \\
 fmincon & 1.366 & 0.061 & 0.083 \\
 fminunc & 1.628 & 0.051 & 0.083 \\
 evaluations & 1.180 & 0.070 & 0.083 \\
 \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
\label{fig:neg-LL}
\end{figure}
On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
\begin{table}[]
\centering
\begin{tabular}{lccc}
\toprule
 & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
 \midrule
 Initial guess & 1.544 & 0.072 & 0.111 \\
 fminsearch & 1.278 & 0.076 & 0.097 \\
 fmincon & 1.577 & 0.062 & 0.097 \\
 fminunc & 1.544 & 0.063 & 0.097 \\
 evaluations & 1.930 & 0.050 & 0.097 \\
 \bottomrule
\end{tabular}
\caption{Different important points for provider A using model 2 and beta proxies.}
\end{table}
